A spiral galaxy's mass distribution uncovered through lensing and dynamics

### 2016-08-19 revised_version_(4.02)_16-07-20/Answer_to_the_referee.txt

Dear Ms. Evripidou,
Dear anonymous referee,

thank you very much for having a detailed look at our paper draft and preparing this helpful report. We made an effort to account for all the referee's comments and to make some of the sections a bit more understandable---we hope you agree. We attach the original referee report below to which we added our answers.

Kind regards,
Wilma Trick

Attachments:
Trick_J1331_Modelling_revised.tex/.pdf - revised paper file ready for publishing (without any marked text or annotations), if the referee agrees.
Trick_J1331_Modelling_revised_all_changes.pdf - file in which all changes with respect to the previous version of the paper are marked (new text = green, deleted text = red, annotations = blue).
Trick_J1331_Modelling_revised_for_referee.pdf - file for the referee with the deleted text excluded to be more readable (new text = green, annotations = blue).

====================================

This is an interesting paper which makes neat use of the combination of stellar
kinematics and strong lensing to investigate the mass structure of the spiral galaxy
J1331.

--> ANSWER: Thanks. It is a very exiting galaxy that's definitely worth exploring.

----------

The introduction could be re-written slightly to emphasise the points that the study
wants to investigate; for instance, the opening paragraph talks about the methods
used rather than the astrophysics that the study is hoping to probe. This could
probably be removed altogether, and the second paragraph promoted to the beginning.

--> ANSWER: That is a good point. We changed the opening paragraph to a general sentence why determining the matter distribution of galaxies is important. We mention the different methods now in the third paragraph.

----------

It would also be nice to include some more discussion of the possibility of a recent
merger in the galaxy's past in the introduction, as this is a really interesting
feature of the galaxy in question and is also a very active topic of research.

--> ANSWER: Good point. 1.) We added a sentence mentioning the important role of mergers in modifying the matter distribution and added some recent references. 2.) We added a short paragraph later in the introduction that points out that J1331 is a special and very interesting galaxy for researching mergers. We also explain better that this merger is one of the reasons why we especially focus on the inner regions of J1331 in our study.

----------

The manuscript in its current form is also slightly longer than necessary at certain
points: for instance, in section 3.2.1, it is not really necessary to present all
the lensing equations (e.g. the time delay, equation 7), and similarly, section
3.3.1 contains a lot of material that is implicit in Cappellari's JAM code, and
therefore does not need to be explained equation by equation here. Section 3.3.4
also rather throws the book at the NFW profile relations – it probably isn't
necessary to include equation 22.

--> ANSWER: We made an effort to remove unnecessary equations in Section 3.2.1, tighten the explanation of the derivation of the Jeans equations in Section 3.3.1 and 3.3.3 and removed big and clumsy mathematical expressions by referring to the explicit equations in the literature instead. In 3.3.2 we refer stronger to the changes we made to Capellari's JAM code and kept the corresponding equations. In Section 3.3.4 we moved equations that are definitions and therefore needed inline to make it shorter; we kept the concentration vs. halo mass relation (former equation 22) and explicitely mention that we will use this later as a prior in our modelling. In general we include a lot of equations and a substantial theory introduction because it is a paper that is potentially interesting for two communities, the lensing and the dynamics community. We wanted to make the paper understandable for both.

----------

From a scientific perspective, in section 4.3.3, the authors comment that the
varying M/L JAM model is unable to reproduce the dynamics when M/L is forced to be
always rising as a function of radius, but it would be interesting to see if the
model could be improved by removing this constraint. Perhaps the authors could add
such a model to this section, or else comment on why they do not attempt it.

--> ANSWER: We have indeed tried a ``mass-follows-light'' JAM model with constant anisotropy and free M/L profile early on in our investigations of J1331. This was unsuccessful to a degree that showing the result in the paper would not be reasonable.  The way how we can generate variable M/L profiles with our MGE mass model is restricted. We have 6 data points and 5 fit M/L parameter within 5 arcsec. This lead to an over-fitting in the inner regions where most of the Gaussians are, while not having enough flexibility at larger radii. (We added a sentence mentioning that in the paper.) The resulting profile was very wiggly, difficult to interpret and most likely unphysical.  As we lay out in the discussion, constraints on a varying stellar M/L ratio should be motivated by stellar population analysis in the future.

----------

In section 4.4.1, the NFW profile is fitted only to the inner data, and then is
shown to not provide a good model for the data beyond that point. This is not
entirely surprising, given that the outer data were not used to constrain the model!
What happens if the NFW profile is fitted to both small- and large- radius data at
once? (Perhaps it is impossible to find a good NFW model across the whole radius
range, but if this is the case, then it should be stated.)

--> ANSWER: Yes, you are completely right. Our initial tests tried of course to fit the whole range of data, but failed. The problem is that we were never able to fit both the central $v_\text{rms}$ dip and the dip around $R'\sim 6''$ with any of the models we tried. If you think this is frustrating, we definitely feel the same way. Our best explanation was, that the spiral arms do weird things to the kinematics around $R'\sim 5-7''$ that cannot be captured by the axisymmtric Jeans models. In this region our MGE models also were not a good fit to the galaxy anymore. Considering also that there are other studies focussing on the outer regions and the counter-rotating core is the most interesting feature, we decided to focus our efforts on the inner regions and try to explain the central kinematics only. We added however a small new section 4.4.4 that discusses that and why modelling attempts to the whole data range fail and what possible next modelling steps should be.

----------

The discussion section is too non-committal and speculative in parts. For instance,
in section 5.1, the M/Ls inferred from a number of the different models are compared
with M/Ls from the literature, but the authors do not make any value judgement
between the different models to come to any firmer conclusions about what they
believe the most convincing description of the IMF to be. At the moment, this
section seems to just be trying to show that their various models can be made to
agree with previous models from the literature, but it would be much more
interesting if some attempt could be made to resolve all the different models (both
in this paper and in previous works) or at least present them in a more coherent
framework, to try to come up with a better picture of the nature of J1331's IMF.

--> ANSWER: This is a valid point of criticism. We thought again about the different models and indications for different IMFs that we collected and came to the conclusion that an IMF slightly less bottom-beavy than the Salpeter IMF is the most likely model for J1331's bulge. We tried to give Section 5.2 (former 5.1) more structure and tweaked the discussion to present arguments for $\Upsilon_{I,*} \sim 4.2$ and and to argue against the alternative models.
We also moved the section that discusses J1331's merger history to the beginning to the discussion section, focussed more on what the merger could have done to J1331's mass distribution and less on modelling failures. All following sections use the background information about mergers to discuss our models.
Our scientific honesty is however, that without further data, we cannot be more commital and some of our statements have to stay in the "speculation regime".

----------

In Section 5.2, the authors could make suggestions for what might be causing the two
$v_{rms}$ dips. Currently, they just state what cannot be the cause, but do not make any
more convincing suggestions – e.g. could it be associated with the possible recent
merger that is explored in Section 5.3? It would be more satisfying if some
suggestions like this could be put forward.

--> ANSWER: Good point. We admit that the text was formulated a bit too negative, and that we can do better in explaining J1331 based on our models than just ruling out things. Also, some of the effects that mergers can have on galaxies could, if they occured in J1331, actually explain some of the peculiar kinematic features of J1331. We tried to re-formulate section 5.3 (former 5.2) and discuss several aspects of the kinematics with respect to the merger history.

----------

While the use of English is impressive given that it is not the main author's mother
tongue, I would also recommend giving the manuscript to a native speaker to correct
the number of grammatical errors that remain.

--> ANSWER: One of the authors is a native speaker and he had a look at the language again. We corrected everything he thought should be corrected. Hopefully it is fine now.

### 2016-09-18 LensingPaper_draft_v4.03.tex
Started version to be uploaded to arXiv

\title[A spiral galaxy's mass distribution uncovered]{A spiral galaxy's mass distribution uncovered through lensing and dynamics}
\author[W.H. Trick, G. van de Ven and A.A. Dutton]{Wilma H. Trick$^{1}$\thanks{E-mail: trick@mpia.de}, Glenn van de Ven$^{1}$ and Aaron A. Dutton$^{1,2}$\\
$^{1}$Max-Planck-Institute for Astronomy, K\"{o}nigstuhl 17, 69117 Heidelberg, Germany\\
$^{2}$New York University Abu Dhabi, PO Box 129188, Abu Dhabi, UAE\\}
\begin{document}

@@

%--------------------------------------------
$I(R',\theta')$ describes the intrinsic and 2D projected light distribution or surface density of the galaxy. Under the assumption that the galaxy is oblate and axisymmetric, and given the inclination angle $inc$ of the galaxy with respect to the observer, MGEs allow an analytic deprojection of the 2-dimensional MGE to get a 3-dimensional axisymmetric light distribution or density $\nu(R,z)$ for the galaxy,
\begin{equation}
\nu(R,z) = \sum_i \nu_{0,i} \exp \left[-\frac{1}{2\sigma_i}\left(R^2 + \frac{z^2}{q_i^2} \right) \right], \label{eq:deprojMGE}
\end{equation}
where $R$ is the distance from the galaxy's short axis and $z$ the height above the galactic plane.\footnote{$(R,z)$ are cylindrical coordinates aligned with the galactic plane. The primed $(R',z')$ denote polar coordinates on the plane of the sky.} The flattening $q_i$ of each axisymmetric 3D Gaussian and its central density $\nu_{0,i}$ follow from the observed 2D axis ratio $q'_i$ and surface density $I_{0,i}$ as
\begin{eqnarray}
q_i^2 &=& \frac{q_i'^2 - \cos^2 (inc)}{\sin^2 (inc)}\\
\nu_{0,i} &=& \frac{q_i' I_{0,i}}{q_i \sqrt{2 \pi \sigma_i^2}}.
\end{eqnarray}
%--------------------------------------------

@@

@@

In this way one can now calculate an unambiguous model prediction for the velocity dispersion tensor $\langle v_i v_j \rangle(R,z) = \langle v_i^2 \rangle(R,z)$ (with $i,j \in \{ R,\phi, z\}$ and $\langle v_i v_j \rangle=0$ if $i\neq j$). To compare it with observations, $\langle v_i^2 \rangle(R,z)$ has to be rotated by the inclination angle $inc$ to the coordinate system of the observer; $(x',y')$ is the plane of the sky and $z'$ the line-of-sight, where $x'$ is alinged with the galaxy's major axis. Taking a light-weighted projection along the line-of-sight gives a model prediction for the line-of-sight velocity second moment $\langle v_\text{los}^2\rangle(x',y')$, which is comparable to actual spectroscopic measurements of the second velocity moment. Details of the derivation of $\langle v_\text{los}^2\rangle(x',y')$ from the Jeans equations using the MGE formalism are laid out in \citet{Cap08} and in the appendix of \citet{GlennEC}. The result for $\langle v_\text{los}^2\rangle(x',y')$ in particular is given in Equation (28) and Equation (A18), respectively.

@@

%============================================
\begin{table}
\centering
\caption{General galaxy parameters of J1331.}
\begin{tabular}{lllr}
\hline
redshift \citep{SWELLSIII}                 & $z_d$ & $0.113$ \\
angular diameter distance & $D_\text{d}$ [Mpc] & $414$ \\
scaling                   & $1~\text{kpc} / 1''$ & $2.006$ \\
position angle from North          & $\phi$ [$^\circ$] & $42.90$\\
average axis ratio & $q'$ & $0.598$\\
average ellipticity & $\epsilon = 1 - q'$ & $0.402$ \\
estimated inclination & $inc$ [$^\circ$] & $70$\\
apparent I-band magnitude & $m_\text{I}$ [mag] & $15.77$ \\
total I-band luminosity & $L_\text{I,tot}$ [$10^{10} L_\odot$] & $5.6$ \\
effective half-light radius & $R_\text{eff}$ [$''$] & $2.6$ \\
& $R_\text{eff}$ [pc]& 5.2 & \\
\hline
\end{tabular}
\label{tab:galaxyparameters}
\end{table}
%============================================

@@

The scaling of the drizzled HST/WFC3 images is  $S \equiv 0.05''/\text{pixel width}$ and the total exposure time $T = 1600$ sec. Each Gaussian in the MGE has a total F814W luminosity $L_i$ (in counts) and a central surface brightness (in counts per pixel) of
\begin{equation}
C_{0,i}\text{[counts/pixel]} = \frac{L_i[\text{counts}]}{2\pi \sigma_i[\text{pixel}]^2 q_i}.
\end{equation}
This is then transformed into an I-band surface brightness (in $\text{mag}\times(1'')^{-2}$) via
\begin{equation}
\mu_{I,0,i} \simeq -2.5 \log_{10}\left( \frac{C_{0,i}\text{[counts/pixel]}}{T[\text{sec}] \times S[''/\text{pixel width}]^2}\right) + Z + C + A_I, \label{eq:muI_}
\end{equation}
where $Z\simeq21.62~\text{mag}$ is the zero-point from \citet{Holtzman}, updated according to \citet{Dolphin,DolphinNew}, for the photometric system of the HST/WFPC2 camera and the F814W filter, plus a correction for the difference in gain between calibration and observation. $C= 0.1~\text{mag}$ corrects for the finite aperture of the WFPC2; and $A_I =0.015~\text{mag}$ is the extinction in the (Landolt) I-band towards J1331, according to the NASA/IPAC Extragalactic Database (NED)\footnote{The NASA/IPAC Extragalactic Database (NED, \url{https://ned.ipac.caltech.edu/}) is operated by the Jet Propulsion Laboratory, California Institute of Technology, under contract with the National Aeronautics and Space Administration. The data for J1331 (SDSS J133140.33+362811.9) was retrieved in October 2013.}. The colour-dependent correction between the F814W filter and the I-band of the UBVRI photometric system is  small \citep{Holtzman} and we neglect it therefore. The last step is to transform the surface brightness $\mu_{I,0,i}$ (in mag) to the I-band surface density $I_{0,i}$ (in $L_\odot$/pc$^2$) of the Gaussian, i.e.,
\begin{eqnarray}
I_{0,i}[L_\odot \text{pc}^{-2}] = \left( 64800/\pi\right)^2 \left(1+z_d \right)^4 10^{0.4\left(M_{\odot,I}-\mu_{I,0,i} \right)},
\end{eqnarray}
where the term with $z_d$ accounts for redshift dimming and $M_{\odot,I}=4.08~\text{mag}$ is the Sun's absolute I-band magnitude \citep{1998gaas.book.....B}. The luminosity $L_i$[counts] and the corresponding surface brightness density $I_{0,i} [L_\odot \text{pc}^{-2}]$ of each Gaussian are given in Table \ref{fig:MGEinnerRegions}.
%--------------------------------------------

%--------------------------------------------
\subsubsection{Inclination, total luminosity and effective radius}
%--------------------------------------------

%--------------------------------------------
To estimate the inclination of J1331 with respect to the observer, we use the observed axis ratio of the flattest ellipse in the IRAF \emph{ellipse} model for J1331, which is $q'=0.42$. This is similar to the disk axis ratio of $q' = 0.40$ found by \citet{SWELLSI}. If a typical thickness of an oblate disk is around $q_0 \sim 0.2$ \citep{1958MeLu2.136....1H}, the inclination follows from 
\begin{equation}
\cos^2 (inc) = \frac{q'^2 - q_0^2}{1 - q_0^2}
\end{equation}
and a correction of $+3^\circ$ \citep{1988ngc..book.....T}. Our estimate for the inclination is therefore $inc \approx 70^\circ$. Given this inclination, the 2-dimensional MGE models can be deprojected into three dimensions (see Section \ref{sec:MGE_theo_deprojection}).

J1331's total I-band luminosity is determined by summing up the luminosity contributions of all the MGE Gaussians for the outer regions (shown as grey lines in Figure \ref{fig:MGEouterRegions}). We find $L_\text{I,tot} \simeq 5.6 \times 10^{10} ~L_\odot$. This corresponds to an apparent magnitude of $m_I = 15.77~\text{mag}$. We determine the circularized effective radius $R_\text{eff}$ of J1331 from the definition $L(<R_\text{eff}) \equiv \frac 12 L_\text{tot}$ and the growth curve $L(<R')$ from the MGE model of the outer regions, where $R'$ is the projected radius on the sky. We find the effective radius to be $R_\text{eff} \simeq 2.6'' \hat{=} 5.2~\text{kpc}$.  All values are summarized in Table \ref{tab:galaxyparameters}.
%--------------------------------------------

@@

%============================================
\begin{figure}
  \centering
  \includegraphics[height=6cm]{fig/lensing_JAM_comparision.ps}
  \caption{Comparison (not a fit!) of the symmetrized stellar $v_\text{rms}$ data of J1331 (blue dots) with JAM models generated from mass distributions which were independently derived from lensing constraints in Section \ref{sec:results_lensing} (red lines). The red solid line corresponds to the lens model for a flat rotation curve ($\alpha = 1$) in Table \ref{tab:bestfitlensmodel}; the red dashed and dash-dotted lines are best fit lens models found analogously from the image positions, but for a fixed rotation curve slope of $\alpha = 1.1$ and $0.9$, respectively. For the JAM modelling best fit MGEs to the lens mass models were used, as well as the observed surface brightness MGE in Table \ref{tab:MGEF814W}, assuming velocity isotropy $\beta_z = 0$ and an inclination of $inc = 70^\circ$. The most reliable constraints are around the Einstein radius (vertical red dotted line); outside of it the model is just an extrapolation.}
  \label{fig:JAM_modelL}
\end{figure}
%============================================

@@

%--------------------------------------------
In this section we create dynamical models for J1331 following the procedure in Sections \ref{sec:model_JAM_JAM}-\ref{sec:model_JAM_compare}. We use the deprojected surface brightness MGE from Table \ref{tab:MGEF814W} for the tracer distribution $\nu(R,z)$ and to generate mass models $\rho(R,z)$. The only exception is the first test, where the mass model comes from lensing constraints.
%--------------------------------------------

@@

%--------------------------------------------
We proceed by modelling the mass distribution with (i) a stellar component, which we get from the light MGE in Table \ref{tab:MGEF814W} (deprojected to the intrinsic $\nu(R,z)$) times a constant stellar mass-to-light ratio $\Upsilon_\text{I,*}$, and (ii) a spherical NFW DM component (see Section \ref{sec:model_JAM_NFW}) with halo scale length $r_s$ and circular velocity $v_{200}$ at the virial radius as free parameters. In the JAM modelling we use a 10-Gaussian MGE fit to the classical NFW profile from Equation \eqref{eq:NFWprofile}.

>>>>

\title[Galaxy mass distribution via lensing \& dynamics]{A spiral galaxy's mass distribution uncovered through lensing and dynamics}
\author[W.H. Trick, G. van de Ven, and A.A. Dutton]{Wilma H. Trick$^{1}$\thanks{E-mail: trick@mpia.de}, Glenn van de Ven$^{1}$ and Aaron A. Dutton$^{1,2}$\\
$^{1}$Max-Planck-Institute for Astronomy, K\"{o}nigstuhl 17, 69117 Heidelberg, Germany\\
$^{2}$New York University Abu Dhabi, PO Box 129188, Abu Dhabi, UAE\\}
\begin{document}

@@

@@

%--------------------------------------------
$I(R',\theta')$ describes the intrinsic and 2D projected light distribution or surface density of the galaxy. Under the assumption that the galaxy is oblate and axisymmetric, and given the inclination angle $\iota$ of the galaxy with respect to the observer, MGEs allow an analytic deprojection of the 2-dimensional MGE to get a 3-dimensional axisymmetric light distribution or density $\nu(R,z)$ for the galaxy,
\begin{equation}
\nu(R,z) = \sum_i \nu_{0,i} \exp \left[-\frac{1}{2\sigma_i}\left(R^2 + \frac{z^2}{q_i^2} \right) \right], \label{eq:deprojMGE}
\end{equation}
where $R$ is the distance from the galaxy's short axis and $z$ the height above the galactic plane.\footnote{$(R,z)$ are cylindrical coordinates aligned with the galactic plane. The primed $(R',z')$ denote polar coordinates on the plane of the sky.} The flattening $q_i$ of each axisymmetric 3D Gaussian and its central density $\nu_{0,i}$ follow from the observed 2D axis ratio $q'_i$ and surface density $I_{0,i}$ as
\begin{eqnarray}
q_i^2 &=& \frac{q_i'^2 - \cos^2 \iota}{\sin^2 \iota}\\
\nu_{0,i} &=& \frac{q_i' I_{0,i}}{q_i \sqrt{2 \pi \sigma_i^2}}.
\end{eqnarray}
%--------------------------------------------

@@

In this way one can now calculate an unambiguous model prediction for the velocity dispersion tensor $\langle v_i v_j \rangle(R,z) = \langle v_i^2 \rangle(R,z)$ (with $i,j \in \{ R,\phi, z\}$ and $\langle v_i v_j \rangle=0$ if $i\neq j$). To compare it with observations, $\langle v_i^2 \rangle(R,z)$ has to be rotated by the inclination angle $\iota$ to the coordinate system of the observer; $(x',y')$ is the plane of the sky and $z'$ the line-of-sight, where $x'$ is alinged with the galaxy's major axis. Taking a light-weighted projection along the line-of-sight gives a model prediction for the line-of-sight velocity second moment $\langle v_\text{los}^2\rangle(x',y')$, which is comparable to actual spectroscopic measurements of the second velocity moment. Details of the derivation of $\langle v_\text{los}^2\rangle(x',y')$ from the Jeans equations using the MGE formalism are laid out in \citet{Cap08} and in the appendix of \citet{GlennEC}. The result for $\langle v_\text{los}^2\rangle(x',y')$ in particular is given in Equation (28) and Equation (A18), respectively.

@@

%============================================
\begin{table}
\centering
\caption{General galaxy parameters of J1331.}
\begin{tabular}{lllr}
\hline
redshift \citep{SWELLSIII}                 & $z_d$ & $0.113$ \\
angular diameter distance & $D_\text{d}$ [Mpc] & $414$ \\
scaling                   & $1~\text{kpc} / 1''$ & $2.006$ \\
position angle from North          & $\phi$ [$^\circ$] & $42.90$\\
average axis ratio & $q'$ & $0.598$\\
average ellipticity & $\epsilon = 1 - q'$ & $0.402$ \\
estimated inclination & $\iota$ [$^\circ$] & $70$\\
apparent I-band magnitude & $m_\text{I}$ [mag] & $15.77$ \\
total I-band luminosity & $L_\text{I,tot}$ [$10^{10} L_\odot$] & $5.6$ \\
effective half-light radius & $R_\text{eff}$ [$''$] & $2.6$ \\
& $R_\text{eff}$ [pc]& 5.2 & \\
\hline
\end{tabular}
\label{tab:galaxyparameters}
\end{table}
%============================================

@@

The scaling of the drizzled HST/WFC3 images is  $S \equiv 0.05''/\text{pixel width}$ and the total exposure time $T = 1600$ sec. Each Gaussian in the MGE has a total F814W luminosity $L_i$ (in counts) and a central surface brightness (in counts per pixel) of
\begin{equation}
C_{0,i}\text{[counts/pixel]} = \frac{L_i[\text{counts}]}{2\pi \sigma_i[\text{pixel}]^2 q_i}.
\end{equation}
This is then transformed into an I-band surface brightness (in $\text{mag}\times(1'')^{-2}$) via
\begin{equation}
\mu_{I,0,i} \simeq -2.5 \log_{10}\left( \frac{C_{0,i}\text{[counts/pixel]}}{T[\text{sec}] \times S[''/\text{pixel width}]^2}\right) + Z + C + A_I, \label{eq:muI_}
\end{equation}
where $Z\simeq21.62~\text{mag}$ is the zero-point from \citet{Holtzman}, updated according to \citet{Dolphin,DolphinNew}, for the photometric system of the HST/WFPC2 camera and the F814W filter, plus a correction for the difference in gain between calibration and observation. $C= 0.1~\text{mag}$ corrects for the finite aperture of the WFPC2; and $A_I =0.015~\text{mag}$ is the extinction in the (Landolt) I-band towards J1331, according to the NASA/IPAC Extragalactic Database (NED)\footnote{The NASA/IPAC Extragalactic Database (NED, \url{https://ned.ipac.caltech.edu/}) is operated by the Jet Propulsion Laboratory, California Institute of Technology, under contract with the National Aeronautics and Space Administration. The data for J1331 (SDSS J133140.33+362811.9) was retrieved in October 2013.}. The colour-dependent correction between the F814W filter and the I-band of the UBVRI photometric system is  small \citep{Holtzman} and we neglect it therefore. The last step is to transform the surface brightness $\mu_{I,0,i}$ (in mag) to the I-band surface density $I_{0,i}$ (in $L_\odot$/pc$^2$) of the Gaussian, i.e.,
\begin{eqnarray}
I_{0,i}[L_\odot \text{pc}^{-2}] = \left( 64800/\pi\right)^2 \left(1+z_d \right)^4 10^{0.4\left(M_{\odot,I}-\mu_{I,0,i} \right)},
\end{eqnarray}
where the term with $z_d$ accounts for redshift dimming and $M_{\odot,I}=4.08~\text{mag}$ is the Sun's absolute I-band magnitude \citep{1998gaas.book.....B}. The luminosity $L_i$[counts] and the corresponding surface brightness density $I_{0,i} [L_\odot \text{pc}^{-2}]$ of each Gaussian are given in Table \ref{tab:MGEF814W}.
%--------------------------------------------

%--------------------------------------------
\subsubsection{Inclination, total luminosity and effective radius} \label{sec:incl_Ltot_Reff}
%--------------------------------------------

%--------------------------------------------
To estimate the inclination of J1331 with respect to the observer, we use the observed axis ratio of the flattest ellipse in the IRAF \emph{ellipse} model for J1331, which is $q'=0.42$. This is similar to the disk axis ratio of $q' = 0.40$ found by \citet{SWELLSI}. If a typical thickness of an oblate disk is around $q_0 \sim 0.2$ \citep{1958MeLu2.136....1H}, the inclination follows from 
\begin{equation}
\cos^2 \iota = \frac{q'^2 - q_0^2}{1 - q_0^2}
\end{equation}
and a correction of $+3^\circ$ \citep{1988ngc..book.....T}. Our estimate for the inclination is therefore $\iota \approx 70^\circ$. Given this inclination, the 2-dimensional MGE models can be deprojected into three dimensions (see Section \ref{sec:MGE_theo_deprojection}). We also assume the inclination angle to be known and fixed to this value in the dynamical modelling in Sections \ref{sec:results_JAM_SB} and \ref{sec:results_JAM_NFW}.

J1331's total I-band luminosity is determined by summing up the luminosity contributions of all the MGE Gaussians for the outer regions (shown as grey lines in Figure \ref{fig:MGEouterRegions}). We find $L_\text{I,tot} \simeq 5.6 \times 10^{10} ~L_\odot$. This corresponds to an apparent magnitude of $m_I = 15.77~\text{mag}$. We determine the circularized effective radius $R_\text{eff}$ of J1331 from the definition $L(<R_\text{eff}) \equiv \frac 12 L_\text{tot}$ and the growth curve $L(<R')$ from the MGE model of the outer regions, where $R'$ is the projected radius on the sky. We find the effective radius to be $R_\text{eff} \simeq 2.6'' \hat{=} 5.2~\text{kpc}$.

All galaxy parameters are summarized in Table \ref{tab:galaxyparameters}.
%--------------------------------------------

@@

%============================================
\begin{figure}
  \centering
  \includegraphics[height=6cm]{fig/lensing_JAM_comparision.ps}
  \caption{Comparison (not a fit!) of the symmetrized stellar $v_\text{rms}$ data of J1331 (blue dots) with JAM models generated from mass distributions which were independently derived from lensing constraints in Section \ref{sec:results_lensing} (red lines). The red solid line corresponds to the lens model for a flat rotation curve ($\alpha = 1$) in Table \ref{tab:bestfitlensmodel}; the red dashed and dash-dotted lines are best fit lens models found analogously from the image positions, but for a fixed rotation curve slope of $\alpha = 1.1$ and $0.9$, respectively. For the JAM modelling best fit MGEs to the lens mass models were used, as well as the observed surface brightness MGE in Table \ref{tab:MGEF814W}, assuming velocity isotropy $\beta_z = 0$ and an inclination of $\iota = 70^\circ$. The most reliable constraints are around the Einstein radius (vertical red dotted line); outside of it the model is just an extrapolation.}
  \label{fig:JAM_modelL}
\end{figure}
%============================================

@@

%--------------------------------------------
In this section we create dynamical models for J1331 following the procedure in Sections \ref{sec:model_JAM_JAM}-\ref{sec:model_JAM_compare}. We use the deprojected surface brightness MGE from Table \ref{tab:MGEF814W} for the tracer distribution $\nu(R,z)$ and to generate mass models $\rho(R,z)$ (assuming the galaxy's inclination angle to be $\iota=70^\circ$; see Table \ref{tab:galaxyparameters} and Section \ref{sec:incl_Ltot_Reff}). The only exception is the first test, where the mass model comes from lensing constraints.
%--------------------------------------------

@@

%--------------------------------------------
We proceed by modelling the mass distribution with (i) a stellar component, which we get from the light MGE in Table \ref{tab:MGEF814W} (deprojected to the intrinsic $\nu(R,z)$ using the fixed inclination angle $\iota=70^\circ$ in Table \ref{tab:galaxyparameters}) times a constant stellar mass-to-light ratio $\Upsilon_\text{I,*}$, and (ii) a spherical NFW DM component (see Section \ref{sec:model_JAM_NFW}) with halo scale length $r_s$ and circular velocity $v_{200}$ at the virial radius as free parameters. In the JAM modelling we use a 10-Gaussian MGE fit to the classical NFW profile from Equation \eqref{eq:NFWprofile}.
